Large scale agile transformations: A literature review

### 2013-01-24 tex/article.tex
Results

\subsection{Typical characteristics of a transformation}

Text only. text. text.

@@

        \raggedright Aligning organization for change  &
             Lack of management support \newline
             Change resistance \newline
             Reverting to old model under pressure \\

        \raggedright\rule{0pt}{0.4cm}Misunderstanding the agile model  &
             Misinterpretation of roles and responsibilities \newline
             Misunderstanding management role in agile \\

        \raggedright\rule{0pt}{0.4cm}Applicability of agile in the organization  &
            Conflicts with business (long term planning) \newline
            Conflicts with other departments (HR) \\

        \raggedright\rule{0pt}{0.4cm}Lack of resources  &
            Lack or training, insufficient resources for coaching \\
        \bottomrule
    \end{tabular}
    \caption{Typical challenges encountered in studies}
    \label{table:challenges}
\end{table}

@@

        \raggedright Organization alignment and leadership  &
             Management support \newline
             Communicating vision for new process \newline
             Demand all organizational units to participate \\

        \raggedright\rule{0pt}{0.4cm}Coaching and community  &
             Create community to make the new practices stick \\

        \raggedright\rule{0pt}{0.4cm}Tailoring and conformity  &
            Invest in tailoring to create the most suitable model \newline
            Conformity clarifies use of the new model \\

        \raggedright\rule{0pt}{0.4cm}Investing in change  &
            Training, consulting, physical spaces, tools \\
        \bottomrule
    \end{tabular}
    \caption{Success factors reported in studies}
    \label{table:success}
\end{table}

>>>>

The most usual way of implementing the change was a stepwise adoption of agile,
which usually included a pilot project. A typical stepwise adoption was to first
create agile teams and introduce basic practices. Having intra-team agile
practices in place made it possible to see how the entire organization would be
affected by the agile way of working.

The central role of management in the change was evident in many studies. This
was typically shown in that the change was initiated by the management and
management took responsibility of the change process. Several studies identified
a champion who was the driver of the change. Some studies reported the change to
be driven by external consultants or a cross organizational work group.

@@

        \raggedright Aligning organization for change  &
             Lack of management support [S1, S5, S13]\newline
             Change resistance [S14, S22, S26] \newline
             Reverting to old model [S4, S11, S23] \\

        \raggedright\rule{0pt}{0.4cm}Misunderstanding the agile model  &
             Wrong application of roles and responsibilities \newline
             [S6, S10, S11, S13, S17, S23, S24] \\

        \raggedright\rule{0pt}{0.4cm}Applicability of agile in the organization  &
            Conflicts with business (eg. planning) [S6, S11, S21] \newline
            Suitability for non-development (testing, maintenance, etc.) [S2, S4, S13]\newline
            Conflicts with other functions [S6, S10, S11, S13] \\

        \raggedright\rule{0pt}{0.4cm}Lack of resources  &
            Lack of training, insufficient resources for coaching \newline
            [S5, S13, S22, S28]\\
        \bottomrule
    \end{tabular}
    \caption{Typical challenges encountered in studies}
    \label{table:challenges}
\end{table}

@@

        \raggedright Organization alignment and leadership  &
             Management support [S8, S9, S10, S13, S16, S19] \newline
             Communicate vision for new process [S7, S19] \newline
             Demand all organizational units to participate [S13, S15, S17, S18, S19, S21] \\

        \raggedright\rule{0pt}{0.4cm}Coaching and community  &
             Create community to make the new practices stick [S4, S6, S7, S28] \\

        \raggedright\rule{0pt}{0.4cm}Tailoring and conformity  &
            Tailor the most suitable model [S8, S11, S20] \newline
            Conformity clarifies use of the new model [S19, S24, S29, S30]\\

        \raggedright\rule{0pt}{0.4cm}Investing in change  &
            Training, consulting, physical spaces, tools [S6, S14, S19]\\
        \bottomrule
    \end{tabular}
    \caption{Success factors reported in studies}
    \label{table:success}
\end{table}
